Computing Entropies with Nested Sampling

### 2017-10-17 talk/ms.tex
Some stuff

\begin{enumerate}
  \item<2-> Generate $N$ points from $\pi$
  \item<3-> Find the worst one (lowest likelihood $L^*$), save it
  \item<4-> Estimate its $X$ using Beta$(N,1)$ distribution\footnote{From order statistics.}
  \item<5-> Record worst particle and its $X$-value, then discard it.
  \item<6-> Replace that point with a new one from $\pi$ but with
        likelihood above $L^*$.
  \item<7-> Repeat steps 2--5 indefinitely.
\end{enumerate}

>>>>

\begin{enumerate}
  \item<2-> Generate $N$ points from $\pi$
  \item<3-> Find the worst one (lowest likelihood $L^*$), save it
  \item<4-> Estimate its $X$ using Beta$(N,1)$ distribution\footnote{From order statistics.}
  \item<5-> Record worst particle and its $X$-value, then discard it.
  \item<6-> Replace that point with a new one from $\pi$ but with
        likelihood above $L^*$.
  \item<7-> Repeat steps 2--5 indefinitely.
\end{enumerate}
\end{frame}

% New slide
\begin{frame}
\frametitle{The sequence of $X$-values}
The sequence of $X$ values, if you transform them, have
a Poisson process distribution with rate $N$.

\begin{align}
-\ln(X_1) &\sim \textnormal{Exponential}(N) \\
-\ln(X_2) &\sim -\ln(X_1) + \textnormal{Exponential}(N) \\
-\ln(X_3) &\sim -\ln(X_2) + \textnormal{Exponential}(N) 
\end{align}

(forgive the notational abuse)

% New slide
\begin{frame}
\frametitle{Poisson process view of NS}

The number of NS iterations taken
to enter a small region (defined by a likelihood threshold) 
as an unbiased estimator of the log-probability
of that region!\vspace{0.7em}

Also, $\pi(\theta)$ can be any distribution (needn't be
a prior) and $L(\theta)$ any scalar function. Opportunities here...

% New slide
\begin{frame}
\frametitle{My algorithm}
To compute $H(\theta) = -\int f(\theta) \log f(\theta) \, d\theta$
when $f$ can be sampled but not evaluated:

\begin{enumerate}
  \item<2-> Generate a `reference point' $\theta_{\rm ref}$ from $f$
  \item<3-> Do a Nested Sampling run with $f$ as ``prior'' and
            minus the distance to $\theta_{\rm ref}$ as
            ``likelihood''.
  \item<4-> Measure how many NS iterations were needed to make the
            distance to $\theta_{\rm ref}$ really small, and divide
            by $N$. That gives an
            unbiased estimate of the
            log-prob near $\theta_{\rm ref}$.
  \item<5-> Repeat steps 1--3 many times.
  \item<6-> Average the estimated log-probs, then apply corrections
            to convert to density.
\end{enumerate}
